### 2014-05-15 lineage-movement.tex
lineage movement

More generally, if we define
\begin{align}
    h(x) = \E[\tau_\rho \given X_0 = x]
\end{align}
then $h$ solves the equation
\begin{align}
    0 = M'(x) h'(x) + \frac{1}{2} M(x) h''(x) - \rho k(x) h(x) + 1 .
\end{align}

The probability that a segment of length $r = \rho \sigma^2$ to one side of the selected locus
does not recombine across time $t$ is $\P\{\tau_\rho > t\}$.
Therefore, if $L_t$ is the length of the nonrecombined segment to one side of the selected locus
after time $t$, then
\begin{align}
    \E[ L_t \given X_0=x ] &= \sigma^2 \int_0^\infty \P\{ \tau_\rho > t \} d\rho \\
\end{align}
The appropriate thing to do is to look at $\E[L_T]$, where $T$ is the coalescence time.

>>>>

More generally, if we define
\begin{align}
    h(x) = \E[\tau_\rho \given X_0 = x]
\end{align}
then $h$ solves the equation
\begin{align}
    -1 = M'(x) h'(x) + \frac{1}{2} M(x) h''(x) - \rho k(x) h(x) .
\end{align}

The probability that a segment of length $r = \rho \sigma^2$ to one side of the selected locus
does not recombine across time $t$ is $\P\{\tau_\rho > t\}$.
Therefore, if $L_t$ is the length of the nonrecombined segment to one side of the selected locus
after time $t$, then
\begin{align}
    \E[ L_t \given X_0=x ] &= \sigma^2 \int_0^\infty \P\{ \tau_\rho > t \} d\rho \\
\end{align}

The appropriate thing to do is to look at $\E[L_T]$, where $T$ is the coalescence time.
Generally, then
\begin{align}
  \P\{ L_t > \rho \} = \P\{ \tau_\rho > T \} .
\end{align}
Do do this properly, we need to run two diffusions.
However, if we let $T$ instead be independent Exponential($\lambda$), then 
\begin{align}
  \ell(x) = \P\{ \tau_\rho > T \given X_0 = x\} 
\end{align}
solves the equation
\begin{align}
  M'(x) \ell'(x) + \frac{1}{2} M(x) \ell''(x) - (\lambda + \rho k(x) ) \ell(x) = \lambda .
\end{align}

\paragraph{Questions:} 
\begin{enumerate}

    \item Can we make any progress analytically with any of these quantities,
      using the fact that
      \[ \frac{1}{2} p''(x) + s(x) p(x)(1-p(x)) = 0 \quad ?\]

    \item Do we get the same system using, say, a Wright--Fisher model?  (I assume so?)

    \item Can we prove convergence of the finite model to this one, under suitable assumptions?  A main difficulty here would be showing that the lineage spends all its time in the part of the range where $p(x)$ does not fluctuate significantly, i.e.\ is not too small\ldots but if this is not true, it would be even more interesting.

\end{enumerate}
